---
title: "ROSeq"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{ROSeq}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# ROSeq - A rank based approach to modeling gene expression

Author: Krishan Gupta

## Introduction

ROSeq - survival of patients using ors on TCGA data

## Installation

The developer version of the R package can be installed with the following R commands:

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install('ORsurv')

## Vignette tutorial

This vignette uses a small simulated data, to demonstrate a standard pipeline. This vignette can be used as a tutorial as well.

## Example

Libraries need to be loaded before running.


```{r setup}
library(ORsurv)
```

```{r data, message=FALSE,warning = FALSE,include=TRUE, cache=FALSE}
matrix_1=matrix(-499:500,100,10)
rownames(matrix_1)=paste("R",1:100,sep="")
colnames(matrix_1)=paste("C",1:10,sep="")
matrix_2=matrix(1:1000,100,10)
rownames(matrix_2)=paste("R",1:100,sep="")
colnames(matrix_2)=paste("C",1:10,sep="")
matrix_3=matrix(1:1000,100,10)
rownames(matrix_3)=paste("R",1:100,sep="")
colnames(matrix_3)=paste("C",1:10,sep="")
t1=-3
t2=3
t3=5
method="cosine"
name1=paste("EXP_new",method,t2,t3,sep="_")
name2=paste("EXP_TCGA_new",method,t2,t3,sep="_")
name3=paste("Survival_plot_new",method,t2,t3,sep="_")
survival_info=matrix(c(1:10,rep(1,5),rep(0,5)),10,2)
rownames(survival_info)=paste("C",1:10,sep="")
colnames(survival_info)=paste("R",1:2,sep="")
month_limit=180
p_limit=2
selected_label=c(1,2,3,4,5)
folder="~/Ahuja_Lab/EXP52_3/"
```

```{r main, message=FALSE,warning = FALSE, include=TRUE, cache=FALSE}
output<-ORsurv(folder=folder,matrix_1=matrix_1,matrix_2=matrix_2,matrix_3=matrix_3,t1=t1,t2=t2,t3=t3,
         name1=name1,name2=name2,name3=name3,survival_info=survival_info,method=method,
         month_limit=month_limit,p_limit=p_limit,selected_label=selected_label)
```

```{r output, message=FALSE,warning = FALSE,include=TRUE, cache=FALSE}
output
```
